Lifting CDCL to Relational Domains

### 2016-10-15 domains.tex
some more on transformers

%-------------------------------------------------------------------------------
\paragraph{Template Polyhedra Abstract Domain}
%
The template polyhedra domain~\cite{sriram} represents sets $X$ of
valuations of a vector of variables $\vec{x}$ such that
$\mat{C}\vec{x}\leq\vec{d}$ for a fixed coefficient matrix $\mat{C}$
and a constant vector $\vec{d}$. The domain of $\vec{d}$ is augmented
by a special element to denote the minimal element $\bot$ of the lattice.
%
The abstraction function is defined as $\alpha(X) = \min \{\vec{d}\mid
\mat{C}\vec{x}\leq\vec{d}, \vec{x}\in X\}$ where $\min$ is
applied component-wise. There are several optimisation-based
techniques for computing the domain
operations~\cite{sriram,GS07b,BJKS15}. In our implementation we use
the strategy iteration approach available in 2LS~\cite{BJKS15}.
%
For notational convenience we will use conjunctions of linear
inequalities, e.g.\ $x_1\geq 0 \wedge x_1-z\leq 30$ to denote elements
of the domain. $\true$ is $\top$ and $\false$ is $\bot$.

@@

%-------------------------------------------------------------------------------
\subsection{Abstract Transformers}
%-------------------------------------------------------------------------------
In a typical abstract interpretation based Galois-connection setting
over an over-approximate domain, every concrete element has a unique
over-approximate representation in the abstract.  Likewise, every
concrete transformer is over-approximated by a unique abstract
transformer.  We now define an abstract deduction transformer.

$\llbracket s \rrbracket^\sharp(a)=\min \{a'\mid a'\sqsubset a, a'\models s\}$

\pscmt{define $a'\models s$}

We define a specialised variant of the transformer to compute deductions w.r.t.\ a given subdomain $L\subseteq A$.

$\llbracket s \rrbracket^\sharp(a,L)=\min \{a'\mid a'\sqsubset a, a'\in L, a'\models s\}$

We have the property $\llbracket s \rrbracket^\sharp(a)\sqsubseteq a\meet\llbracket s \rrbracket^\sharp(a,L)$.

For example,
$a=(0\leq y \leq 1 \wedge 5\leq z)$
$\llbracket x=y+z\rrbracket^\sharp(a,\{x\})=(x\geq 6)$, whereas
$\llbracket x=y+z\rrbracket^\sharp(a,\{y\})=\top$.

@@

\pscmt{TODO from here}

>>>>

%-------------------------------------------------------------------------------
\paragraph{Template Polyhedra Abstract Domain}
%
The template polyhedra domain~\cite{sriram} represents sets $X$ of
valuations of a vector of variables $\vec{x}$ such that
$\mat{C}\vec{x}\leq\vec{d}$ for a fixed coefficient matrix $\mat{C}$
and a constant vector $\vec{d}$. The domain of $\vec{d}$ is augmented
by a special element to denote the minimal element $\bot$ of the lattice.
%
The abstraction function is defined as $\alpha(X) = \min \{\vec{d}\mid
\mat{C}\vec{x}\leq\vec{d}, \vec{x}\in X\}$ where $\min$ is
applied component-wise. There are several optimisation-based
techniques for computing the domain
operations~\cite{sriram,GS07b,BJKS15}. In our implementation we use
the strategy iteration approach available in 2LS~\cite{BJKS15}.
%
The concretisation $\gamma(\vec{d})$ is the set $\{\vec{x}\mid
\mat{C}\vec{x}\leq\vec{d}\}$; $\gamma(\bot)=\emptyset$.
%
For notational convenience we will use conjunctions of linear
inequalities, e.g.\ $x_1\geq 0 \wedge x_1-z\leq 30$ to denote elements
of the domain. $\true$ is $\top$ and $\false$ is $\bot$.

@@

%-------------------------------------------------------------------------------
\subsection{Abstract Transformers}
%-------------------------------------------------------------------------------
%In a typical abstract interpretation based Galois-connection setting
%over an over-approximate domain, every concrete element has a unique
%over-approximate representation in the abstract.  Likewise, every
%concrete transformer is over-approximated by a unique abstract
%transformer.  We now define an abstract deduction transformer.

An abstract transformer transforms an abstract value $a$ through a
statement $s$, i.e.\ it \emph{deduces} information from $a$ and $s$.
The best abstract transformer is
\[\llbracket s
\rrbracket^\sharp(a)=\min \{a'\mid a'\models s\}\] 
where we write
$a\models s$ if $\forall \vec{y}\in\gamma(a): (s[\vec{y}/\vec{x}]
\equiv \true)$, i.e.\ the constraint $s$ is valid when evaluated over
all values $\vec{y}$ of its variables $\vec{x}$ in the concretisation
of $a$. Any abstract transformer that computes a non-minimal element
is still a sound over-approximating transformer and can be used in our
algorithm.

To make our algorithm efficient, we have to focus abstract
transformers on performing only the minimally necessary
work. 
%
We thus define a specialised variant of the transformer to compute
deductions w.r.t.\ a given subdomain $L\sqsubseteq A$, $\bot,\top \in L$.
\[\llbracket s \rrbracket^\sharp(a,L)=\min \{a'\mid a'\in L, a'\models s\}\]
We have the property $\llbracket s \rrbracket^\sharp(a)\sqsubseteq \llbracket s \rrbracket^\sharp(a,L)$.

For example, for
$a=(0\leq y \leq 1 \wedge 5\leq z)$ we have
$\llbracket x=y+z\rrbracket^\sharp(a,\{x\})=(x\geq 6)$, whereas
$\llbracket x=y+z\rrbracket^\sharp(a,\{y\})=\top$.

@@
